Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-17 vesicle_code/docs/permeableVes/main.tex
yny2

In Figures~\ref{fig:contractingComposite}a
and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
different permeability rates and membrane is color coded by the permeable flux (red for influx and blue for eflux).
Figure~\ref{fig:contractingComposite}c
shows the corresponding reduced area as a function of the vesicles' location. 
The reduced area in Figure~\ref{fig:contractingComposite}c and f shows that the vesicle always inflates
before it reaches the neck.  However, if the
semi-permeability rate is too low, the vesicle is too large when it
reaches the narrowest part of the channel, and it is unable to pass. In
Figures~\ref{fig:contractingComposite}d
and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
different imposed maximum velocities, and
Figure~\ref{fig:contractingComposite}f shows that the reduced area as a
function of the vesicles' location. At low velocities, the vesicle
inflates similar to the unbounded parabolic flow example, and it is
unable to pass through the constrictions. However, higher flow rates
result in additional deflation and the vesicle passes through the
contraction.

>>>>

In Figures~\ref{fig:contractingComposite}a
and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
different permeability rates. 
Figure~\ref{fig:contractingComposite}c
shows the corresponding reduced area as a function of the vesicles' location. 
The reduced area in Figure~\ref{fig:contractingComposite}c and f shows that the vesicle always inflates gradually
before it reaches the neck, where vesicle quickly deflates.  
{\bf YNY: inflates over seconds but deflates over ms?}
However, if the
semi-permeability rate is too low, the vesicle is too large when it
reaches the narrowest part of the channel, and it is unable to pass. In
Figures~\ref{fig:contractingComposite}d
and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
different imposed maximum velocities, and
Figure~\ref{fig:contractingComposite}f shows that the reduced area as a
function of the vesicles' location. At low velocities, the vesicle
inflates similar to the unbounded parabolic flow example, and it is
unable to pass through the constrictions. However, higher flow rates
result in additional deflation and the vesicle passes through the
contraction.
